Manhattan Plot

### 2021-09-16 code/manhattan_animated.Rmd
updated data by week

@@

@@

@@

@@

  vacc = vacc_tot %>%
    filter(classe_age != "00-19") %>%
    group_by(codgeo) %>%
    summarise(effectif_1_inj = sum(effectif_1_inj),
              population_carto = sum(population_carto)) %>%
    ungroup() %>%
    mutate(taux_1_inj = effectif_1_inj / population_carto)

@@

```{r, echo = F, message = F, warning = F}
data = NULL
for (i in 18:34){
  data = bind_rows(
    data,
    make_data_covid(i, classe_age = "00-19") %>%
      arrange(theme, id) %>%
      mutate (pos = row_number(),
              week = i)
  )
}

@@

```{r, echo = F, message = F, warning = F}
data = NULL
for (i in 2:34){
  data = bind_rows(
    data,
    make_data_covid(i, classe_age = "20-39") %>%
      arrange(theme, id) %>%
      mutate (pos = row_number(),
              week = i)
  )
}

@@

```{r, echo = F, message = F, warning = F}
data = NULL
for (i in 2:34){
  data = bind_rows(
    data,
    make_data_covid(i, classe_age = "40-54") %>%
      arrange(theme, id) %>%
      mutate (pos = row_number(),
              week = i)
  )
}

@@

```{r, echo = F, message = F, warning = F}
data = NULL
for (i in 2:34){
  data = bind_rows(
    data,
    make_data_covid(i, classe_age = "55-64") %>%
      arrange(theme, id) %>%
      mutate (pos = row_number(),
              week = i)
  )
}

@@

```{r, echo = F, message = F, warning = F}
data = NULL
for (i in 2:34){
  data = bind_rows(
    data,
    make_data_covid(i, classe_age = "65-74") %>%
      arrange(theme, id) %>%
      mutate (pos = row_number(),
              week = i)
  )
}

@@

```{r, echo = F, message = F, warning = F}
data = NULL
for (i in 2:34){
  data = bind_rows(
    data,
    make_data_covid(i, classe_age = "75+et+%2B") %>%
      arrange(theme, id) %>%
      mutate (pos = row_number(),
              week = i)
  )
}

@@

```{r, message = F, echo = F, warning = F}
data = make_data_covid_cumul(22:28)

@@

```{r, message = F, warning = F, echo = F}
data = read_csv2(url("https://datavaccin-covid.ameli.fr/explore/dataset/donnees-de-vaccination-par-epci/download/?format=csv&refine.semaine_injection=2021-22&timezone=Europe/Berlin&lang=fr&use_labels_for_header=true&csv_separator=%3B")) %>%
  plyr::rbind.fill(read_csv2(url("https://datavaccin-covid.ameli.fr/explore/dataset/donnees-de-vaccination-par-epci/download/?format=csv&refine.semaine_injection=2021-27&timezone=Europe/Berlin&lang=fr&use_labels_for_header=true&csv_separator=%3B"))) %>%
  plyr::rbind.fill(read_csv2(url("https://datavaccin-covid.ameli.fr/explore/dataset/donnees-de-vaccination-par-epci/download/?format=csv&refine.semaine_injection=2021-34&timezone=Europe/Berlin&lang=fr&use_labels_for_header=true&csv_separator=%3B")))
data = data %>%
  filter(classe_age != "TOUT_AGE") %>%
  group_by(semaine_injection, classe_age) %>%
  summarise(population_carto = sum(population_carto),
            effectif_cumu_1_inj = sum(effectif_cumu_1_inj, na.rm = T)) %>%
  ungroup() %>%
  mutate(taux_cumu_1_inj = round(100* effectif_cumu_1_inj / population_carto, 2)) %>%
  pivot_wider(id_cols = semaine_injection, names_from = classe_age, values_from = taux_cumu_1_inj)
# pivot_wider(id_cols = classe_age, names_from = semaine_injection, values_from = taux_cumu_1_inj)
data %>%
  pander()
data %>%
  amBarplot(x = "semaine_injection", y = c("00-19", "20-39", "40-54", "55-64", "65-74", "75 et +")) %>%
  # amBarplot(x = "classe_age", y = c("2021-22", "2021-27", "2021-34")) %>%
  amOptions(legend = TRUE, export = TRUE)
```

>>>>

  wk1 = wk-1

@@

  if (wk1/10 <1){
    wk1 = paste0("0", wk1)
  }

@@

  vacc$taux_cumu_1_inj[is.na(vacc$taux_cumu_1_inj)] <- 0
  vacc$taux_1_inj[is.na(vacc$taux_cumu_1_inj)] <- 0

  if (variable == "taux_cumu_1_inj"){
    LOG_1107 = LOG_fact %>% select(-taux_cumu_1_inj) %>% inner_join(vacc) %>% mutate(taux_cumu_1_inj = as.factor(binarisation(taux_cumu_1_inj, 0.25)))
    EMP_1107 = EMP_fact %>% select(-taux_cumu_1_inj) %>% inner_join(vacc) %>% mutate(taux_cumu_1_inj = as.factor(binarisation(taux_cumu_1_inj, 0.25)))
    FAM_1107 = FAM_fact %>% select(-taux_cumu_1_inj) %>% inner_join(vacc) %>% mutate(taux_cumu_1_inj = as.factor(binarisation(taux_cumu_1_inj, 0.25)))
    REV_1107 = REV_fact %>% select(-taux_cumu_1_inj) %>% inner_join(vacc) %>% mutate(taux_cumu_1_inj = as.factor(binarisation(taux_cumu_1_inj, 0.25)))
    ACT_1107 = ACT_fact %>% select(-taux_cumu_1_inj) %>% inner_join(vacc) %>% mutate(taux_cumu_1_inj = as.factor(binarisation(taux_cumu_1_inj, 0.25)))
    FOR_1107 = FOR_fact %>% select(-taux_cumu_1_inj) %>% inner_join(vacc) %>% mutate(taux_cumu_1_inj = as.factor(binarisation(taux_cumu_1_inj, 0.25)))
    POP_1107 = POP_fact %>% select(-taux_cumu_1_inj) %>% inner_join(vacc) %>% mutate(taux_cumu_1_inj = as.factor(binarisation(taux_cumu_1_inj, 0.25)))
    IMM_1107 = IMM_fact %>% select(-taux_cumu_1_inj) %>% inner_join(vacc) %>% mutate(taux_cumu_1_inj = as.factor(binarisation(taux_cumu_1_inj, 0.25)))
    GEO_1107 = GEO_fact %>% select(-taux_cumu_1_inj) %>% inner_join(vacc) %>% mutate(taux_cumu_1_inj = as.factor(binarisation(taux_cumu_1_inj, 0.25)))
  }else if (variable == "taux_1_inj"){

    if (classe_age == "tous"){
      vacc_com1 = read_csv2(url(paste0("https://datavaccin-covid.ameli.fr/explore/dataset/donnees-de-vaccination-par-commune/download/?format=csv&refine.semaine_injection=2021-", wk1, "&refine.classe_age=TOUT_AGE&timezone=Europe/Berlin&lang=fr&use_labels_for_header=true&csv_separator=%3B"))) %>%
        mutate(codgeo = as.factor(commune_residence)) %>%
        mutate(taux_cumu_1_inj = as.numeric(taux_cumu_1_inj))

      vacc1 = read_csv2(url(paste0("https://datavaccin-covid.ameli.fr/explore/dataset/donnees-de-vaccination-par-epci/download/?format=csv&refine.semaine_injection=2021-", wk1, "&refine.classe_age=TOUT_AGE&timezone=Europe/Berlin&lang=fr&use_labels_for_header=true&csv_separator=%3B"))) %>%
        mutate(codgeo = as.factor(epci)) %>%
        mutate(taux_cumu_1_inj = as.numeric(taux_cumu_1_inj)) %>%
        plyr::rbind.fill(vacc_com1)
    }else{
      vacc_com1 = read_csv2(url(paste0("https://datavaccin-covid.ameli.fr/explore/dataset/donnees-de-vaccination-par-commune/download/?format=csv&refine.classe_age=", classe_age, "&refine.semaine_injection=2021-", wk1, "&timezone=Europe/Berlin&lang=fr&use_labels_for_header=true&csv_separator=%3B"))) %>%
        mutate(codgeo = as.factor(commune_residence)) %>%
        mutate(taux_cumu_1_inj = as.numeric(taux_cumu_1_inj))

      vacc1 = read_csv2(url(paste0("https://datavaccin-covid.ameli.fr/explore/dataset/donnees-de-vaccination-par-epci/download/?format=csv&refine.semaine_injection=2021-", wk1, "&refine.classe_age=", classe_age, "&timezone=Europe/Berlin&lang=fr&use_labels_for_header=true&csv_separator=%3B"))) %>%
        mutate(codgeo = as.factor(epci)) %>%
        mutate(taux_cumu_1_inj = as.numeric(taux_cumu_1_inj)) %>%
        plyr::rbind.fill(vacc_com1)
    }

    vacc1$taux_cumu_1_inj[is.na(vacc1$taux_cumu_1_inj)] <- 0
    vacc1$taux_1_inj[is.na(vacc1$taux_cumu_1_inj)] <- 0

    vacc = vacc %>%
      inner_join(vacc1, by = "codgeo") %>%
      mutate(pop = population_carto.x - effectif_cumu_1_inj.y,
             taux_1_inj = pop / effectif_1_inj.x)

    LOG_1107 = LOG_fact %>% select(-taux_cumu_1_inj) %>% inner_join(vacc) %>% mutate(taux_cumu_1_inj = as.factor(binarisation(as.numeric(taux_1_inj, 0.25))))
    EMP_1107 = EMP_fact %>% select(-taux_cumu_1_inj) %>% inner_join(vacc) %>% mutate(taux_cumu_1_inj = as.factor(binarisation(as.numeric(taux_1_inj, 0.25))))
    FAM_1107 = FAM_fact %>% select(-taux_cumu_1_inj) %>% inner_join(vacc) %>% mutate(taux_cumu_1_inj = as.factor(binarisation(as.numeric(taux_1_inj, 0.25))))
    REV_1107 = REV_fact %>% select(-taux_cumu_1_inj) %>% inner_join(vacc) %>% mutate(taux_cumu_1_inj = as.factor(binarisation(as.numeric(taux_1_inj, 0.25))))
    ACT_1107 = ACT_fact %>% select(-taux_cumu_1_inj) %>% inner_join(vacc) %>% mutate(taux_cumu_1_inj = as.factor(binarisation(as.numeric(taux_1_inj, 0.25))))
    FOR_1107 = FOR_fact %>% select(-taux_cumu_1_inj) %>% inner_join(vacc) %>% mutate(taux_cumu_1_inj = as.factor(binarisation(as.numeric(taux_1_inj, 0.25))))
    POP_1107 = POP_fact %>% select(-taux_cumu_1_inj) %>% inner_join(vacc) %>% mutate(taux_cumu_1_inj = as.factor(binarisation(as.numeric(taux_1_inj, 0.25))))
    IMM_1107 = IMM_fact %>% select(-taux_cumu_1_inj) %>% inner_join(vacc) %>% mutate(taux_cumu_1_inj = as.factor(binarisation(as.numeric(taux_1_inj, 0.25))))
    GEO_1107 = GEO_fact %>% select(-taux_cumu_1_inj) %>% inner_join(vacc) %>% mutate(taux_cumu_1_inj = as.factor(binarisation(as.numeric(taux_1_inj, 0.25))))
  }

@@

  wk1 = wks[1] - 1

  if (wk1/10 <1){
      wk1 = paste0("0", wk1)
  }

  vacc_com1 = read_csv2(url(paste0("https://datavaccin-covid.ameli.fr/explore/dataset/donnees-de-vaccination-par-commune/download/?format=csv&refine.semaine_injection=2021-", wk1, "&timezone=Europe/Berlin&lang=fr&use_labels_for_header=true&csv_separator=%3B"))) %>%
      mutate(codgeo = as.factor(commune_residence)) %>%
      mutate(taux_cumu_1_inj = as.numeric(taux_cumu_1_inj))

    vacc1 = read_csv2(url(paste0("https://datavaccin-covid.ameli.fr/explore/dataset/donnees-de-vaccination-par-epci/download/?format=csv&refine.semaine_injection=2021-", wk1, "&timezone=Europe/Berlin&lang=fr&use_labels_for_header=true&csv_separator=%3B"))) %>%
      mutate(codgeo = as.factor(epci)) %>%
      mutate(taux_cumu_1_inj = as.numeric(taux_cumu_1_inj)) %>%
      plyr::rbind.fill(vacc_com1) %>%
      filter(!(classe_age %in% c("00-19", "TOUT_AGE"))) %>%
      select(codgeo, classe_age, population_carto, effectif_cumu_1_inj) %>%
      group_by(codgeo) %>%
      summarise(population_carto = sum(population_carto),
                effectif_cumu_1_inj = sum(effectif_cumu_1_inj)) %>%
      ungroup()

@@

    vacc_agg = vacc_tot %>%
      select(codgeo, classe_age, population_carto, effectif_1_inj) %>%
      filter(!(classe_age %in% c("00-19", "TOUT_AGE"))) %>%
      group_by(codgeo) %>%
      summarise(effectif_1_inj = sum(effectif_1_inj, na.rm = T)) %>%
      ungroup()

  vacc = vacc_agg %>%
    inner_join(vacc1) %>%
    mutate(taux_1_inj = effectif_1_inj/(population_carto - effectif_cumu_1_inj))

@@

```{r, echo = F, message = F, warning = F}
data = NULL
for (i in 18:34){
  data = bind_rows(
    data,
    make_data_covid(i, variable = "taux_1_inj", classe_age = "00-19") %>%
      arrange(theme, id) %>%
      mutate (pos = row_number(),
              week = i)
  )
}

@@

```{r, echo = F, message = F, warning = F}
data = NULL
for (i in 2:34){
  data = bind_rows(
    data,
    make_data_covid(i, variable = "taux_1_inj", classe_age = "20-39") %>%
      arrange(theme, id) %>%
      mutate (pos = row_number(),
              week = i)
  )
}

@@

```{r, echo = F, message = F, warning = F}
data = NULL
for (i in 2:34){
  data = bind_rows(
    data,
    make_data_covid(i, variable = "taux_1_inj", classe_age = "40-54") %>%
      arrange(theme, id) %>%
      mutate (pos = row_number(),
              week = i)
  )
}

@@

```{r, echo = F, message = F, warning = F}
data = NULL
for (i in 2:34){
  data = bind_rows(
    data,
    make_data_covid(i, variable = "taux_1_inj", classe_age = "55-64") %>%
      arrange(theme, id) %>%
      mutate (pos = row_number(),
              week = i)
  )
}

@@

```{r, echo = F, message = F, warning = F}
data = NULL
for (i in 2:34){
  data = bind_rows(
    data,
    make_data_covid(i, variable = "taux_1_inj", classe_age = "65-74") %>%
      arrange(theme, id) %>%
      mutate (pos = row_number(),
              week = i)
  )
}

@@

```{r, echo = F, message = F, warning = F}
data = NULL
for (i in 2:34){
  data = bind_rows(
    data,
    make_data_covid(i, variable = "taux_1_inj", classe_age = "75+et+%2B") %>%
      arrange(theme, id) %>%
      mutate (pos = row_number(),
              week = i)
  )
}

@@

```{r, message = F, echo = F, warning = F}
data = make_data_covid_cumul(22:27)

@@

```{r, message = F, warning = F, echo = F}
data = read_csv2(url("https://datavaccin-covid.ameli.fr/explore/dataset/donnees-de-vaccination-par-epci/download/?format=csv&refine.semaine_injection=2021-22&timezone=Europe/Berlin&lang=fr&use_labels_for_header=true&csv_separator=%3B")) %>%
  plyr::rbind.fill(read_csv2(url("https://datavaccin-covid.ameli.fr/explore/dataset/donnees-de-vaccination-par-epci/download/?format=csv&refine.semaine_injection=2021-27&timezone=Europe/Berlin&lang=fr&use_labels_for_header=true&csv_separator=%3B"))) %>%
  plyr::rbind.fill(read_csv2(url("https://datavaccin-covid.ameli.fr/explore/dataset/donnees-de-vaccination-par-epci/download/?format=csv&refine.semaine_injection=2021-34&timezone=Europe/Berlin&lang=fr&use_labels_for_header=true&csv_separator=%3B")))
data = data %>%
  filter(classe_age != "TOUT_AGE") %>%
  group_by(semaine_injection, classe_age) %>%
  summarise(population_carto = sum(population_carto),
            effectif_cumu_1_inj = sum(effectif_cumu_1_inj, na.rm = T)) %>%
  ungroup() %>%
  mutate(taux_cumu_1_inj = round(100* effectif_cumu_1_inj / population_carto, 2)) %>%
  pivot_wider(id_cols = semaine_injection, names_from = classe_age, values_from = taux_cumu_1_inj)
# pivot_wider(id_cols = classe_age, names_from = semaine_injection, values_from = taux_cumu_1_inj)
data %>%
  pander()
data %>%
  amBarplot(x = "semaine_injection", y = c("00-19", "20-39", "40-54", "55-64", "65-74", "75 et +")) %>%
  # amBarplot(x = "classe_age", y = c("2021-22", "2021-27", "2021-34")) %>%
  amOptions(legend = TRUE, export = TRUE, main = "Couverture vaccinale par tranche d'âge et par semaine")
```
